### 2017-04-30 thesis/latex/thesis.tex
Remove old variable-ts code from project.
Improve how thesis figures are generated.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-ghosts}
  \caption{Snapshots of model over the course of a simulation. Bothbound states are depicted immediately after binding events. Onebound states depict the conformation with the highest unbound binding domain between binding events. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-ghosts}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-x-trajectory}
  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-x-trajectory}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: make these figures compare better.}
  \end{minipage}
  \hspace{.1cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
    \caption{Histogram of simulated stepping times using ideal dynein parameters.}
  \end{minipage}\\
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Experimental dynein step size from \cite{weihongpaper}.}
  \end{minipage}
  \hspace{.1cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-velocity.pdf}
    \caption{Experimental dynein step time from \cite{weihongpaper}}
  \end{minipage}
  \label{fig:final-histograms}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-y-trajectory}
  \caption{Unbound binding domain position over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-y-trajectory}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.2\textwidth]{../../plots/stepping-ghost}
  \caption{Snapshots of model over the course of a simulation. Bothbound states are depicted immediately after binding events. Onebound states depict the conformation with the highest unbound binding domain between binding events. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-ghosts}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{../../plots/x-trajectory_thesis}
  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-x-trajectory}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_time_histogram_thesis}
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-velocity.pdf}
    \caption{Experimental dynein step time from \cite{weihongpaper}}
    \label{fig:final-histograms}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{../../plots/y-trajectory_thesis}
  \caption{Unbound binding domain position over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-y-trajectory}
\end{figure}
